### 2017-03-08 paper/oopsla17-submission/introduction.tex
init paper
blurb about contributions

\section{Evaluation}
\label{sec:evaluation}

>>>>

\section{Introduction}
\label{sec:introduction}

\subsection{Contributions}
\label{sec:contributions}
Thus, we identify the following novel contributions of our work.
%
\begin{enumerate}
\item An experimental evaluation of state-of-the-art type-error
  localization techniques based not on expert \emph{opinion}, but
  on the eventual \emph{fix} implemented by a novice user.
  %
  \ES{need to explain \emph{why} this is superior..}
\item A machine learning approach to \emph{modeling} (novice) type
  errors that can outperform the state-of-the-art by 10--30\% in
  localizing errors.
  %
  Our model can be trained on a relatively small amount of data --- we
  used a single class of around 50 students --- and appears to
  generalize to other instances of the same class.
  %
  \ES{and hopefully completely separate classes!}
  %
  In contrast to many approaches to \emph{fault localization} from the
  software engineering community, our model does not use any linguistic
  modeling techniques, \eg \emph{n-grams} over the token stream; rather,
  it relies entirely on features of the abstract syntax tree and a
  partial typing derivation.
  %
  \ES{if there's time, investigate adding Wes' n-gram model}
\end{enumerate}

### 2017-03-08 paper/oopsla17-submission/learning.tex
blurb about contributions

The first issue we must tackle is formulating our learning task in
machine learning terms.
%
We are given programs over $e$, but the learning algorithms expect to work
with \emph{feature vectors} --- vectors of real numbers, where each
column describes a particular aspect of the input.
%
Thus, our first task is to convert programs to feature vectors.

@@

\subsection{Models}
\label{sec:models}
\ES{TODO: trade-off between ease of training/interpreting and
  complexity, \ie actually fitting the data..}

\paragraph{Linear models}
The simplest model we investigate is a linear model, which learns a
linear function of the features.
%
The goal is to learn a set of weights $W$ and biases $b$ such that the
function
%
$$
y = Wx + b
$$
%
effectively maps feature vectors $x$ to labels $y$.

@@

Linear models are popular for their ease of training and of interpreting
the resulting model; however, they can be quite limited in their
applicability.
%
As the name implies, linear models will perform poorly when asked to
learn an inherently \emph{nonlinear} function.
%
This limitation can be mitigated to some extent by adding more features
to the model (\eg combinations of the existing features \ES{CITE?}), but
the fundamental issue remains.

>>>>

The first issue we must tackle is formulating our learning task in
machine learning terms.
%
We are given programs over \lang, but the learning algorithms expect to work
with \emph{feature vectors} --- vectors of real numbers, where each
column describes a particular aspect of the input.
%
Thus, our first task is to convert programs to feature vectors.

@@

\subsection{Learning Algorithms}
\label{sec:models}
\ES{TODO: mention that this is a SUPERVISED, CLASSIFICATION problem}
%
There are a large number of learning algorithms to choose from, existing
on a spectrum that balances expressiveness with ease of training (and of
interpreting the learned model).
%
In this section we present the learning algorithms we will investigate,
beginning with the simplest.
%
For each algorithm, we describe \ES{TODO...}

\paragraph{Logistic regression}
The simplest model we investigate is logistic regression, which learns a
linear function of the features.
%
The goal is to learn a set of weights $W$ and biases $b$ such that the
function
%
$$
y = Wx + b
$$
%
effectively maps feature vectors $x$ to labels $y$.

@@

Linear models like logistic regression are popular for their ease of
training and of interpreting the resulting model; however, they can be
limited in their applicability.
%
As the name implies, linear models may perform poorly when asked to
learn an inherently \emph{nonlinear} function.
%
This limitation can be mitigated to some extent by adding more features
to the model (\eg combinations of the existing features \ES{CITE?}), but
the fundamental issue remains.
